\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-19 doc/flexiblesusy-paper.tex
altered wording describing E6SSM mass comparison.

The \fs generated NUHM \ESSM\ spectrum generator has also been
compared against a handwritten one for a constrained version of the
\ESSM \cite{Athron:2009ue, Athron:2009bs, Athron:2012pw}.  The
$\beta$-functions were systematically compared in unit tests and were
found to match within numerical precision.  The handwritten code
doesn't include full one-loop self-energies or tadpoles, so tests on
these were not carried out.  Although the generators assume different
constraints and solve the boundary value problem with completely
different algorithms they could be compared by using the output of
the CE$_6$SSM generator as an input to \fs and the spectra were found
to be in reasonable agreement ($\approx 10\%$), given the different
levels of precision.

>>>>

The \fs generated NUHM \ESSM\ spectrum generator has also been
compared against a handwritten one for a constrained version of the
\ESSM \cite{Athron:2009ue, Athron:2009bs, Athron:2012pw}.  The
$\beta$-functions were systematically compared in unit tests and were
found to match within numerical precision.  The handwritten code
doesn't include full one-loop self-energies or tadpoles, so tests on
these were not carried out.  Although the generators assume different
constraints and solve the boundary value problem with completely
different algorithms they could be compared by using the output of
the CE$_6$SSM generator as an input to \fs and the spectra were found
to be in reasonable agreement  given the different levels of precision with deviatiuons in the mass spectra $\lesssim 10\%$.
